---
title: "Compare datasets"
author: "Claus Dethlefsen (CDN)"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Compare datasets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(knitr.duplicate.label = "allow")
```

## Setup training data base
In case you have not already setup a training database please run
```{r}
NNtraining::createTrainingDB()
```
Assuming that you work on the R-server, this will copy the training datasets from the `NNtraining` package into your home-directory in a subfolder called `training`. If the files already exists, nothing will happen. The training folder can then be used to read/write from, as if it was a real trial folder on the p-drive.


## Compare datasets

Imagine that in a trial, you want to compare all datasets at two occasions. Interest is in detecting exactly what has changed, e.g. when getting close to the Database Lock.

Here, we will emulate changed datasets and keep the comparison dataset in memory. If datasets were to be compared between locations, a non-standard location, could be added to the `nnaccess`-object using the function `sasaccess`.
```{r Simulate change in datasets, include=FALSE}
library(NNBiostat)
mytrial <- nnaccess("0001", root="~/training")

#This is how a different version could be added as folder. Not used in the example.
mytrial$dm_external <- sasaccess("~/training/nn1234/nn1234-0001/dm/data/external_data")

# retrieve names of all adam datasets
alladam <- mytrial$adam()

# Here, we will only pick a few
alladam <- alladam[c(11,18,21)]

## read adsl and make some modifications, emulating that something has changed between two versions
adsl.modified <- mytrial$adam("adsl") %>% 
    filter(SUBJID != "128001") %>% # oops, we forgot a subject
    mutate(COUNTRY = recode(COUNTRY, "USA"="US"))  # oops, wrote US instaed of USA

## read adlb and make some modifications
adlb.modified <- mytrial$adam("adlb") %>%
  mutate(AVAL = ifelse(AVAL<1, .5, AVAL))  # AVAL wrong value

## read advs, but leave it unchanged.  
advs.modified <- mytrial$adam("advs") # no change

```


```{r sdtm}
library(NNBiostat)
library(NNcompare)
mytrial <- nnaccess("0001", root="~/training")

all <- mytrial$adam()
all <- all[c(11,18,21)] # to simplify, we just pick 3 datasets in this vignette

## we could use a for-loop to compare all files. However, since we have kept the
## modified datasets as objects in memory, we will do the comparison "by hand"
#for (domain in all) {
#
#    cat("Parsing:",domain,"\n")
#    d.new <- mytrial$adam(domain, ext="derived")
#    #d.old <- mytrial$dm_external(paste0("2021_01_21/", domain), ext="derived")
#
#    compare <- comparedf(d.new,d.old)
#    compare.sum <- summary(compare)
#
#    export(x=compare.sum,db=mytrial,type='html', filename = tools::file_path_sans_ext(domain),
#           subfolder="compare_data")
#}

adsl <- mytrial$adam("adsl")
compare.adsl <- comparedf( adsl, adsl.modified, by="USUBJID")
compare.adsl.sum <- summary(compare.adsl)
export(x=compare.adsl.sum, db=mytrial, type='html', filename = "adsl", subfolder="compare_data")

adlb <- mytrial$adam("adlb")
compare.adlb <- comparedf( adlb, adlb.modified, by=c("USUBJID","PARAM","VISITNUM","ATPTN","ASEQ"))
compare.adlb.sum <- summary(compare.adlb)
export(x=compare.adlb.sum, db=mytrial, type='html', filename = "adlb", subfolder="compare_data")

# advs <- mytrial$adam("advs")
# compare.advs <- comparedf( advs, advs.modified, by="USUBJID")
# compare.advs.sum <- summary(compare.advs)
# export(x=compare.advs.sum, db=mytrial, type='html', filename = "advs", subfolder="compare_data")

```
The default location of the outputs are in the program/parprog subfolder of the instance. In this case, the outputs are redirected to a subfolder of this called `compare_data`.

To summarise the summaries,
```{r summary}
path <- paste0(attr(mytrial,"nninst")$paths$program,"/parprog/compare_data")
file <- "overall_summary"

# prepare overall summary report of short summary files
combined_summary <- combineDFComp(path = path, filename = file)
```
This creates an html-file with a row for each comparison and a hyperlink to the detailed report created.

